
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TCGAgistic

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/TCGAgistic)](https://CRAN.R-project.org/package=TCGAgistic)
[![R-CMD-check](https://github.com/CCICB/TCGAgistic/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CCICB/TCGAgistic/actions/workflows/R-CMD-check.yaml)
[![r-universe status badge](https://CCICB.r-universe.dev/badges/TCGAgistic)](https://CCICB.r-universe.dev/ui#package:TCGAgistic)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8115633.svg)](https://doi.org/10.5281/zenodo.8115633)
<!-- badges: end -->

The goal of TCGAgistic is to easily load gistic copy-number analysis for TCGA cohorts into R

## Installation

Install TCGAgistic from R universe:

``` r
# Install TCGAgistic from R:
install.packages('TCGAgistic', repos = c('https://ccicb.r-universe.dev', 'https://cloud.r-project.org'))
```

Alternatively, you can install the development version from github:

``` r
# install.packages("remotes")
remotes::install_github('CCICB/TCGAgistic')
```

## Quick Start


### Visualising TCGA copy number alterations

Load the GISTIC dataset and visualise results

```{r}
library(TCGAgistic)
library(maftools)

# Load dataset
gistic <- tcga_gistic_load("ACC", source = "Firehose", cnLevel = "all")

# Visualise results
gisticChromPlot(gistic)
```

### List all available datasets
```{r example}
library(TCGAgistic)

# Check available datasets
tcga_gistic_available()
```


## How it works

TCGAgistic streams `rds` files from github, located in the [TCGAgisticDB](https://github.com/CCICB/TCGAgisticDB) package, into your local R session

